\section{Do Developers Discover New Tools On The Toilet?}

\subsection{Abstract}

Maintaining awareness of useful tools is a
substantial challenge for developers. Physical newsletters are a simple technique to inform developers about
tools. In this paper, we evaluate such a technique, called
Testing on the Toilet, by performing a mixed-methods
case study. We first quantitatively evaluate how effective this technique is by applying statistical causal inference over six years of data about tools used by thousands of developers. We then qualitatively contextualize these results by interviewing and surveying 382 developers, from authors to editors to readers. We found
that the technique was generally effective at increasing
software development tool use, although the increase
varied depending on factors such as the breadth of applicability of the tool, the extent to which the tool has
reached saturation, and the memorability of the tool
name.

\subsection{What were they trying to do}

Investigate if people learn about new tools when they're in the toilet.

\subsection{What did they do}

Print 1-page newsletters written by developers and post them in restrooms. This is called "Testing on the Toilet" at Google. Conducted interviews and qualitative analysis.

\subsection{What did they learn}

The technique was generally effective at increasing software development tool use, although the increase varied depending on facts such as the breadth of applicability of the tool, the extend to which tool has reached saturation and the memorability of the tool name.

% a lot of these tools mentioned as examples probably would be under my use-case (cause they're not JAM-stack), so its reasonable to talk about breadth of applicability

% Personally, I'm unable to stop thinking about code and better solutions, and I barely have time between projects. Going to the toilet is often the little "break/sitdown" I get, and being unable to stop thinking about code (possibly wanting to immediately get back on my desk and implement the ideal solution to get it over with), I look up tools on my phone and research how to go about solutions. 
