\section{How Do Professional Developers Comprehend Software?}

\subsection{Abstract}

Research in program comprehension has considerably evolved over the past two decades. However, only little is known about how developers practice program comprehension under time and project pressure, and which methods and tools proposed by researchers are used in industry. This paper reports on an observational study of 28 professional developers from seven companies, investigating how developers comprehend software. In particular we focus on the strategies followed, information needed, and tools used. We found that developers put themselves in the role of end users by inspecting user interfaces. They try to avoid program comprehension, and employ recurring, structured comprehension strategies depending on work context. Further, we found that standards and experience facilitate comprehension. Program comprehension was considered a subtask of other maintenance tasks rather than a task by itself. We also found that face-to-face communication is preferred to documentation. Overall, our results show a gap between program comprehension research and practice as we did not observe any use of state of the art comprehension tools and developers seem to be unaware of them. Our findings call for further careful analysis and for reconsidering research agendas.

\subsection{What were they trying to do}

Investigate how developers comprehend software and the strategies followed, information needed and tools used

The goal of this study is to qualitatively explore \& review the state of the practice in program comprehension and learn how programmers in industry comprehend programs. We aim at gaining deep insights into program comprehension practice, examining the usage of research results in practice, validating findings of similar studies, and overcoming limitations of earlier studies.

\begin{itemize}
    \item Which strategies (including steps and activities) do developers follow to comprehend programs?
    \item Which sources of information do developers use during program comprehension?
    \item Which information is missing?
    \item Which tools do developers use when understanding programs and how?
\end{itemize}

\subsection{What did they do}

Observational study (along with interviews) of 28 professional developers from seven companies who did their normal tasks and informed researchers that they would perform comprehension. Emphasis on distinguish between realism and replication.

\subsection{What did they learn}

Developers put themselves in the role of end users by inspecting user interfaces. They try to avoid comprehending the program and only apply structured strategies depending on work context. Developers sometimes try to avoid comprehending programs. Instead, they clone source code and adapt it to fulfill their current task. They have discussions with peers over reading documentation (if there). Further, standards and experience also play a part in comprehension. The results show a gap between program comprehension research and practice as no use of comprehension tools were seen.
